Comparison of Fast Imaging Architectures for Large, Multi-scale, Hierarchical Aperture Arrays

### 2024-06-09 ms.tex
Update on Overleaf.

\section{Mathematical Notation}

@@

The observed phenomena of radio transients span orders of magnitude in timescales -- provide examples \cite{Pietka+2015}.

>>>>

The paper is organised as follows. In \S\ref{sec:notation}, the mathematical notation describing the measurements and imaging process is established. \S\ref{sec:motivation} describes the scientific and technical motivations for this paper. \S\ref{sec:computational-cost} describes the metric of computational cost density in discovery phase space based on which we compare different imaging architectures described in \S\ref{sec:img-archs}. The multi-scale imaging architecture options for intra- and inter-station data processing are described in sections \ref{sec:inter-station-arch} and \ref{sec:inter-station-arch}, respectively. \S\ref{sec:results} presents a summary of the results, and conclusions are presented in \S\ref{sec:conclusion}.

\section{Mathematical Notation}\label{sec:notation}

@@

The observed phenomena of radio transients span orders of magnitude in timescales -- provide examples \citep{Pietka+2015,Chandra+2016}.
